Analysis-ready VCF at Biobank scale using Zarr

### 2025-04-01 paper.tex
Closes #313
Finish up data access stuff

% The VCF Zarr specification is available on GitHub at
% \url{https://github.com/sgkit-dev/vcf-zarr-spec/}.
% The SAIGE prototype is available at \url{https://github.com/Will-Tyler/SAIGE}
% and all other code for running benchmarks, analyses and creating
% plots in this article is available at
% \url{https://github.com/sgkit-dev/vcf-zarr-publication}.
% Vcf2zarr is freely available under the terms of the Apache 2.0
% license as part of the \texttt{bio2zarr}
% suite (\url{https://github.com/sgkit-dev/bio2zarr/}; 
% biotoolsID=bio2zarr; RRID=SCR\_026481)
% and can be installed from the Python Package Index
% (\url{https://pypi.org/project/bio2zarr/}).
% Vcztools (\url{https://github.com/sgkit-dev/vcztools/};
% biotoolsID=vcztools; RRID=SCR\_026482)
% is freely available under the terms of the Apache 2.0
% license and can be installed from the Python Package Index
% (\url{https://pypi.org/project/vcztools/}).

\section{Data availability}

% Your manuscript lacks a 'Data availability' section and we require it; could
% you please create one and list all the datasets you have used in your case
% studies along with direct URLs (better: DOIs, if available) to these datasets
% (not the associated manuscript, but directly the dataset's main page, for user
% accessibility purposes).
The datasets used for the case studies in this article are described/available at:
Genomics England aggV2: \url{https://re-docs.genomicsengland.co.uk/aggv2/};
Future Health Data Release 9: 
\url{https://ourfuturehealth.gitbook.io/our-future-health/data/data-releases/2024-data-releases/release-9};
All of Us CDRv7:
\url{gs://fc-aou-datasets-controlled/v7/wgs/short\_read/snpindel/acaf\_threshold_v7.1/vcf/},
described at 
\url{https://support.researchallofus.org/hc/en-us/articles/4616869437204-Controlled-CDR-Directory-Archived-C2022Q4R13-CDRv7};
Norway Spruce: data release pending;
SARS-CoV-2 Viridian: \url{https://doi.org/10.6084/m9.figshare.28360031.v2}.

>>>>

\section{Data availability}
The public datasets used in this paper can be found by the following
accessions:
1) Genomics England aggV2~\cite{gel-aggv2} 
which is under controlled access and researchers can apply for access
here~\citep{gel-join};
2) Our Future Health data release 9~\cite{ofhdatarelease9},
which is under controlled access and researchers can apply for access here~\citep{ofh-apply-for-access};
3) All of Us CDRv7~\citep{aou-cdrv7}
which is under controlled access and researchers can apply for access
here~\citep{aou-apply};
4) The Norway Spruce dataset can be found here~\cite{plantgenie};
5) the SARS-CoV-2 Viridian data \cite{kelleher2025viridian}.
